Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-06-13 bbbq_article.tex
Can split PDF
Can make
Figures are separated from text
Main, figures and supmat is nicely separated
Add black-and-white imageses, progress https://github.com/richelbilderbeek/bbbq_article/issues/221

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.8\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{bbbq_1_smart_results/fig_f_tmh_2_panel.png}
    \label{fig:bbbq_1_smart_results}
  \end{subfigure}

  \begin{subfigure}[t]{0.35\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{bbbq_1_smart_results/fig_hydrophobicity_mhc1.png}
    \label{fig:hydrophobicity_1}
  \end{subfigure}  
  \hfill
  \begin{subfigure}[t]{0.35\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{bbbq_1_smart_results/fig_hydrophobicity_mhc2.png}
    \label{fig:hydrophobicity_2}
  \end{subfigure}  
  \caption{ \textbf{Over-presentation of TMH-derived epitopes on most MHC-I and -II haplotypes}
    \textbf{(A)} 
    The percentage of epitopes for MHC-I and -II haplotypes that are predicted to 
    overlap with TMHs for the proteomes of SARS-CoV-2 (top row), human (middle 
    row) and \emph{M. tuberculosis} (bottom row).
    The red lines indicate the percentages as expected by chance.
    See supplementary Tables \ref{tab:tmh_binders_mhc1} and \ref{tab:tmh_binders_mhc2}
    for the exact TMH and  epitope counts.
    \textbf{(B-C)}
    Correlation between the percentages of predicted TMH-derived epitopes
    and the hydrophobicity score of all predicted epitopes for MHC-I \textbf{(B)}
    and MHC-II haplotypes \textbf{(C)}. Red curve: linear regression analysis. 
    Labels are shorthand for the HLA haplotypes,
    see the supplementary Table \ref{tab:haplotype_abbreviations} for the names.
  }
\end{figure}

@@

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{ncbi_peregrine_results/fig_conservation.png}
    \label{fig:conservation}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{ncbi_peregrine_results/fig_f_snps_found_and_expected.png}
    \label{fig:f_snps_found_and_expected}
  \end{subfigure}

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{ncbi_peregrine_results/fig_conservation_per_spanner.png}
    \label{fig:conservation_per_spanner}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{ncbi_peregrine_results/fig_f_tmh_ncbi_per_spanner.png}
    \label{fig:f_tmh_ncbi_per_spanner}
  \end{subfigure}

  \begin{subfigure}[t]{\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{ncbi_peregrine_results/fig_f_snps_found_and_expected_per_spanner.png}
    \label{fig:f_snps_found_and_expected_per_spanner}
  \end{subfigure}
  \caption{ \textbf{Membrane proteins with multiple TMHs are evolutionary more conserved than proteins with only a single TMH.}
      \textbf{(A)} 
      The number of SNPs in TMHs as expected by chance 
      and observed in the dbSNP database, 
      for TMPs with one TMH (single-spanners) and multiple TMHs (multi-spanners).
      Percentages show the relative conservation
      of SNPs in TMHs found.
      \textbf{(B)} 
      Distribution of the proportion of amino acids residing
      in the plasma membrane. 
      \textbf{(C)} 
      Percentage of SNPs found in TMPs predicted to have only a single
      (left) or multiple (right) TMHs.
        Each point shows for one protein the predicted percentage of TMH ($x$-axis) and the observed occurrence of SNPs being located within a TMH ($y$-axis). The dashed diagonal lines show the line of equality (i.e., equal conservation of TMHs and soluble protein regions). The red line indicates a linear fit, the gray area its 95\% confidence interval.
     }
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\section{Supplementary materials}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{bianchi_et_al_2017_results/fig_1a.png}
    \label{fig:bianch_et_al_2017_1a}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{bbbq_1_smart_results/fig_f_tmh_2_human_mhc1.png}
    \label{fig:bilderbeek_et_al_2021_1a}
  \end{subfigure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_smart_results/fig_f_tmh_mhc1_2_normalized.png}
  \caption{
    Normalized proportion of MHC-I epitopes overlapping with TMHs
    for human, viral and bacterial proteomes.
    Legend: covid = SARS-CoV-2,
    human = \emph{Homo sapiens}, 
    myco = \emph{Mycobacterium tuberculosis}
  }
  \label{fig:f_tmh_mhc1_normalized}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_smart_results/fig_f_tmh_mhc2_2_normalized.png}
  \caption{
    Normalized proportion of MHC-II epitopes overlapping with TMHs
    for human, viral and bacterial proteomes.
    Legend: covid = SARS-CoV-2,
    human = \emph{Homo sapiens}, myco = \emph{Mycobacterium tuberculosis}
  }
  \label{fig:f_tmh_mhc2_normalized}
\end{figure}

>>>>

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Figures}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage

% No page number on this page
\thispagestyle{empty}

\begin{figure}[!htbp]
  \centering
  \begin{subfigure}[t]{0.8\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{bbbq_1_smart_results/fig_f_tmh_2_panel_bw.png}
    \label{fig:bbbq_1_smart_results}
  \end{subfigure}

  \begin{subfigure}[t]{0.35\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{bbbq_1_smart_results/fig_hydrophobicity_mhc1_bw.png}
    \label{fig:hydrophobicity_1}
  \end{subfigure}  
  \hfill
  \begin{subfigure}[t]{0.35\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{bbbq_1_smart_results/fig_hydrophobicity_mhc2_bw.png}
    \label{fig:hydrophobicity_2}
  \end{subfigure}  
  \caption{ \textbf{Over-presentation of TMH-derived epitopes on most MHC-I and -II haplotypes}
    \textbf{(A)} 
    The percentage of epitopes for MHC-I and -II haplotypes that are predicted to 
    overlap with TMHs for the proteomes of SARS-CoV-2 (top row), human (middle 
    row) and \emph{M. tuberculosis} (bottom row).
    The red lines indicate the percentages as expected by chance.
    See supplementary Tables \ref{tab:tmh_binders_mhc1} and \ref{tab:tmh_binders_mhc2}
    for the exact TMH and  epitope counts.
    \textbf{(B-C)}
    Correlation between the percentages of predicted TMH-derived epitopes
    and the hydrophobicity score of all predicted epitopes for MHC-I \textbf{(B)}
    and MHC-II haplotypes \textbf{(C)}. Red curve: linear regression analysis. 
    Labels are shorthand for the HLA haplotypes,
    see the supplementary Table \ref{tab:haplotype_abbreviations} for the names.
  }
\end{figure}

% Process all floats before going to a next page
\clearpage

% No page number on this page
\thispagestyle{empty}

% Process all floats before going to a next page
\clearpage

% No page number on this page
\thispagestyle{empty}

\begin{figure}[!htbp]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{ncbi_peregrine_results/fig_conservation.png}
    \label{fig:conservation}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{ncbi_peregrine_results/fig_f_snps_found_and_expected_bw.png}
    \label{fig:f_snps_found_and_expected}
  \end{subfigure}

% Process all floats before going to a next page
\clearpage

% No page number on this page
\thispagestyle{empty}

\begin{figure}[!htbp]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{ncbi_peregrine_results/fig_conservation_per_spanner.png}
    \label{fig:conservation_per_spanner}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{ncbi_peregrine_results/fig_f_tmh_ncbi_per_spanner.png}
    \label{fig:f_tmh_ncbi_per_spanner}
  \end{subfigure}

  \begin{subfigure}[t]{\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{ncbi_peregrine_results/fig_f_snps_found_and_expected_per_spanner_bw.png}
    \label{fig:f_snps_found_and_expected_per_spanner}
  \end{subfigure}
  \caption{ \textbf{Membrane proteins with multiple TMHs are evolutionary more conserved than proteins with only a single TMH.}
      \textbf{(A)} 
      The number of SNPs in TMHs as expected by chance 
      and observed in the dbSNP database, 
      for TMPs with one TMH (single-spanners) and multiple TMHs (multi-spanners).
      Percentages show the relative conservation
      of SNPs in TMHs found.
      \textbf{(B)} 
      Distribution of the proportion of amino acids residing
      in the plasma membrane. 
      \textbf{(C)} 
      Percentage of SNPs found in TMPs predicted to have only a single
      (left) or multiple (right) TMHs.
        Each point shows for one protein the predicted percentage of TMH ($x$-axis) and the observed occurrence of SNPs being located within a TMH ($y$-axis). The dashed diagonal lines show the line of equality (i.e., equal conservation of TMHs and soluble protein regions). The red line indicates a linear fit, the gray area its 95\% confidence interval.
     }
\end{figure}

% Process all floats before going to a next page
\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\appendix
\section{Supplementary materials}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{bianchi_et_al_2017_results/fig_1a_bw.png}
    \label{fig:bianch_et_al_2017_1a}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{bbbq_1_smart_results/fig_f_tmh_2_human_mhc1_bw.png}
    \label{fig:bilderbeek_et_al_2021_1a}
  \end{subfigure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_smart_results/fig_f_tmh_mhc1_2_normalized_bw.png}
  \caption{
    Normalized proportion of MHC-I epitopes overlapping with TMHs
    for human, viral and bacterial proteomes.
    Legend: covid = SARS-CoV-2,
    human = \emph{Homo sapiens}, 
    myco = \emph{Mycobacterium tuberculosis}
  }
  \label{fig:f_tmh_mhc1_normalized}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_smart_results/fig_f_tmh_mhc2_2_normalized_bw.png}
  \caption{
    Normalized proportion of MHC-II epitopes overlapping with TMHs
    for human, viral and bacterial proteomes.
    Legend: covid = SARS-CoV-2,
    human = \emph{Homo sapiens}, myco = \emph{Mycobacterium tuberculosis}
  }
  \label{fig:f_tmh_mhc2_normalized}
\end{figure}
